|

### 2021-08-18 paper/dcpo_demsupport.Rmd
corrected the legend and cross-reference of the plots

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the second analysis of @Claassen2020b.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing Solt's [-@Solt2020a; -@Solt2020b] DCPO model, which unlike Claassen's [-@Claassen2019] model does not dichotomize ordinal responses.  The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (democracy and corruption), and they reproduce that article's findings.
The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
In all four models, the positive coefficients for democratic support are no longer statistically significant.
The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.

@@

```{r mocFormatResult-AJPS}
result_pooled <- bind_rows(
    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Pooled~OLS",
           model = "Model 1 (Pooled OLS)")

result_gmm <- bind_rows(
    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "System~GMM",
           model = "Model 3 (System GMM)")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = rep(
            c("Democracy\n (t-1)",
              "Democracy\n (t-2)",
              "Support\n (t-1)",
              "Log GDP\n per capita\n (t-1)",
              "GDP per\n capita growth\n (t-1)",
              "Regional\n democracy\n (t-1)",
              "Percent\n Muslim\n (t-1)",
              "Resource\n dependence\n (t-1)"),
            time = 6), 
        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
        submodel = factor(submodel, levels = c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
    )

result_regime <- bind_rows(
    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Pooled~OLS",
           model = "Model 2 (Pooled OLS)")

result_regimeGmm <- bind_rows(
    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data")
)%>% 
    mutate(type = "System~GMM",
           model = "Model 4 (System GMM)")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = rep(
            c("Democracy\n (t-1)",
              "Democracy\n (t-2)",
              "Support\n demo only\n (t-1)",
              "Support\n auto only\n (t-1)",
              "Log GDP\n per capita\n (t-1)",
              "GDP per\n capita growth\n (t-1)",
              "Regional\n democracy\n (t-1)",
              "Percent\n Muslim\n (t-1)",
              "Resource\n dependence\n (t-1)"),
            time = 6), 
        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))

@@

df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
  mutate(term = index_coefName[term0], 
           term = factor(term, levels = unique(index_coefName)))

ajps_caption <- "Replications of Claassen (2020a), Table 1, 128."

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO"),
                     labels=c("Point Estimates Only", "Uncertainty & More Data", "Uncertainty & DCPO")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(-0.06, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 9),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-5, "pt"),
          legend.key.size = unit(8, "mm"),
          plot.title = element_text(hjust = 1.4),
          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
  guides(color = guide_legend(override.aes = list(size=.3))) +
  ggtitle("Dependent Variable: Level of Democracy") +
  labs(caption = ajps_caption)

@@

In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [47, Table 1, 49, Table 2].
The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy. 
However, the middle results demonstrate that this thermostatic effect, too, does not  hold after the measurement uncertainty is accounted for. 
And again, the righthand results reveal that the additional data of our extension do not provide support for the original conclusion.
<!-- In fact, once uncertainty is taken into account, the models of @Claassen2020b detect very little pattern in the year-to-year changes of public support for democracy at all. -->

@@

These null results have a number of important substantive implications.
First, they underscore that recognizing the conditional aspects of the classic argument regarding democracy and democratic support is crucial.
With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
There is some empirical evidence for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
On the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
Whether these conditional relationships exist among the newly available latent-variable data on democracy and democratic support remain questions for future research.

@@

# Data Recollection and Uncertainty in Control Variables {#dgp}

Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to achieve a primary replication [@Grossman2020] based on survey data summarized in @Claassen2020a and @Claassen2020b's Dataverse files.

Specifically, we are not able to identify 5 country-year surveys, including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".

@@

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    theme_bw() +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only",
                              "Uncertainty & More Data",
                              "Uncertainty & DCPO"),
                     labels=c("Point Estimates Only",
                              "Uncertainty & More Data",
                              "Uncertainty & DCPO")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(0.006, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 8),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-5, "pt"),
          legend.key.width = unit(4.5, "mm"),
          legend.key.height = unit(7, "mm"),
          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
  guides(color = guide_legend(override.aes = list(size=.3))) +
  ggtitle("Dependent Variable: Change in Public Democratic Support") +
  labs(caption = apsr_caption)
```

>>>>

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the models of @Claassen2020b.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.^[We also attempted to make fuller use of the available survey data by employing the DCPO model [@Solt2020a], which unlike the [@Claassen2019] model does not dichotomize ordinal responses.  The better fit of the DCPO model to these data [see @Solt2020a, 10-12] and the additional information it incorporates, however, did not yield substantively different results; see the Supplemental Information.]

@@

Figure \@ref(fig:plot-fullAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy [@Claassen2020a, Table 1, 128].
The lighter, lefthand set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty by using only the point estimates of public democratic support and the other variables measured with quantified error (democracy and corruption), and they reproduce that article's findings.
The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
In all four models, the positive coefficients for democratic support are no longer statistically significant.
The darker, righthand results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on our expanded dataset; this change works to increase the number of observations analyzed as well.
Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.

@@

```{r mocFormatResult-AJPS}
result_pooled <- bind_rows(
    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Pooled~OLS",
           model = "Model 1 (Pooled OLS)")
result_gmm <- bind_rows(
    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "System~GMM",
           model = "Model 3 (System GMM)")
result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = rep(
            c("Democracy\n (t-1)",
              "Democracy\n (t-2)",
              "Support\n (t-1)",
              "Log GDP\n per capita\n (t-1)",
              "GDP per\n capita growth\n (t-1)",
              "Regional\n democracy\n (t-1)",
              "Percent\n Muslim\n (t-1)",
              "Resource\n dependence\n (t-1)"),
            time = 6), 
        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
        submodel = factor(submodel, levels = c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
    )
result_regime <- bind_rows(
    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Pooled~OLS",
           model = "Model 2 (Pooled OLS)")
result_regimeGmm <- bind_rows(
    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data")
)%>% 
    mutate(type = "System~GMM",
           model = "Model 4 (System GMM)")
result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = rep(
            c("Democracy\n (t-1)",
              "Democracy\n (t-2)",
              "Support\n demo only\n (t-1)",
              "Support\n auto only\n (t-1)",
              "Log GDP\n per capita\n (t-1)",
              "GDP per\n capita growth\n (t-1)",
              "Regional\n democracy\n (t-1)",
              "Percent\n Muslim\n (t-1)",
              "Resource\n dependence\n (t-1)"),
            time = 6), 
        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))

@@

df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
  mutate(term = index_coefName[term0], 
           term = factor(term, levels = unique(index_coefName)))
ajps_caption <- "Replications of Claassen (2020a), Table 1, 128."
small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    theme_bw() +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(-0.06, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 9),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-5, "pt"),
          legend.key.size = unit(8, "mm"),
          plot.title = element_text(hjust = 1.4),
          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
  guides(color = guide_legend(override.aes = list(size=.3))) +
  ggtitle("Dependent Variable: Level of Democracy") +
  labs(caption = ajps_caption)

@@

In Figure \@ref(fig:plot-fullAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [47, Table 1, 49, Table 2].
The negative coefficient estimates for change in liberal democracy in the lefthand set of results, which do not take uncertainty into account, imply that the immediate effect of a increase in the level of democracy is a decline in public support for democracy and of a decrease in democracy an expansion of support---that democratic support indeed does respond thermostatically to democracy. 
However, the middle results demonstrate that this thermostatic effect, too, does not  hold after the measurement uncertainty is accounted for. 
And again, the righthand results reveal that the additional data of our extension do not provide support for the original conclusion.
<!-- In fact, once uncertainty is taken into account, the models of @Claassen2020b detect very little pattern in the year-to-year changes of public support for democracy at all. -->

@@

These null results have a number of important substantive implications.
First, they underscore that it is crucial to recognize the conditional aspects of the classic theory regarding democracy and democratic support.
With regard to how levels of democracy affect public support, even the early proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
There is some empirical evidence for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
On the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
Whether these conditional relationships exist among the newly available latent-variable data on democracy and democratic support remain questions for future research.

@@

# Replication Notes {#dgp}

Replicating the analyses of @Claassen2020a and @Claassen2020b while incorporating the quantified uncertainty in their variables was not possible from those article's Dataverse files.
Instead, it required re-collecting all of the data employed in those articles directly from their original sources, that is, in the terminology of @Grossman2020, it required a primary replication rather than a secondary one.
We describe this process here.

First, we identified the variable names of each survey item in each survey dataset as well as their corresponding values. 
We then used the `DCPOtools` R package to automate the process of generating a dataset of survey marginals.
Due to revisions to the underlying datasets (and, possibly, transcription errors), we were not able to locate 5 country-year-items: including South Sudan in Arab Barometer Wave 4, Dominican Republic in 2003 Latinobarometer, XXXX, and Spain in 2005 Latinobarometer. 
In addition, we still have different sample size and number of respondents answering supportively by following approaches of cleanning data and treatment of non-responses described in @Claassen2020a's supplementatry materials.
Specifically, we used Claassen's year coding to recode 85 unmatching country-year observations and added one more item "strong leader 2" in Arabbarometer which has different response categories but was conflated into "strong leader 1".

@@

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only",
                              "Uncertainty & More Data",
                              "Uncertainty & DCPO"),
                     labels=c("Point Estimates Only",
                              "Uncertainty & More Data",
                              "Uncertainty & DCPO")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(0.006, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 8),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-5, "pt"),
          legend.key.width = unit(4.5, "mm"),
          legend.key.height = unit(7, "mm"),
          plot.caption = element_text(size = 10, hjust = 0.2, margin = margin(t=15))) +
  guides(color = guide_legend(override.aes = list(size=.3))) +
  ggtitle("Dependent Variable: Change in Public Democratic Support") +
  labs(caption = apsr_caption)
```
